Shared Subspace Models for Multi-Group Covariance Estimation

### 2019-02-22 paper/JRSSB/response/response.tex

\begin{resp}
We believe that after these revisions that the behavior of our method is well described.  In particular the paper now includes:
\begin{itemize}
\item Discussion of the convergence on the EM algorithm.  We describe $\sqrt{n}$-consistent initial values for the shared subspace estimator which improve convergence to more optimal modes.
\item A theorem about the behavior of the goodness of fit estimator when $n << p$.  The goodness of fit test can be used to identify whether the inferred subspace is indeed reasonable.  
\item A conjecture about the accuracy of the shared subspace estimator in the small n, large p setting.  We provide a lower bound on the asymptotic bias of our estimator, prove that the lower bound holds exactly when the data from each groups are identically distributed and show in simulation that we exceed this bound.  
\end{itemize}
\end{resp}

\bibliographystyle{chicago}
\bibliography{../refs}
